---
title: "EDA_Airline_review"
author: "Bugra Duman"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## R Markdown


```{r Loading, include=FALSE}
review <- readr::read_csv('skytrax.csv')
library(tidyr)
library(tidyverse)
library(tidytext)
library(tm)
library(stringi)
library(ggthemes)
library(scorecard)
```

## Including Plots

You can also embed plots, for example:

```{r  NA, echo=FALSE}
#Cleaning NAs
#Cleaning NAs
r<- review[complete.cases(review$airline),]

```

We can start exploring our data
```{r Glimpse}

tibble::glimpse(r)

```
Dataset includes detailed score and overall score, besides score we also have detailes about trip such as aircraft and traveller type.Lets start with numbers than categorical values.




```{r Score}
r <- one_hot(r,var_encode = 'recommended')

r_score <- r %>%
  select(airline,overall,seat_comfort,cabin_service,food_bev,entertainment,ground_service,value_for_money)

head(r_score)
```


```{r Most Reviewed}
numberof_reviews_airline <- r_score %>%  group_by(airline) %>% count(airline) %>% dplyr::arrange(desc(n)) 
  ggplot(numberof_reviews_airline[1:20,],aes(x=reorder(airline,-n), y=n)) + 
    geom_bar(stat = "identity") +
    coord_flip()+
    ggtitle("Top 20 Most Reviewed Airlines")+
    theme_fivethirtyeight()
```

Apperantly Cathay Pacific and British Airlines passengers are writing the most about the flight.



```{r Overall scoring}
overall_mean <- r_score %>%  drop_na() %>% 
  group_by(airline) %>% 
  summarise(Overall_Mean=mean(overall)) %>% 
  arrange(desc(Overall_Mean)) %>% head(20)


ggplot(overall_mean,aes(x=reorder(airline,-(Overall_Mean)),y=Overall_Mean),na.rm = TRUE)+
  geom_bar(width=.5,stat = "identity",na.rm = TRUE)+
  coord_flip()

to_do scale_y duzelt


```

Out of all airlines Aegean Airlines from Greece gets the highest points from passengers, one remarakle point over here is The Big 4 Middle East/Gulf airlines (Emirates, Etihad, Qatar, Turkish) are performing relativly low when we compare with others.Note(In our dataset there is no review for Etihad)





```{r Cabin Scoring}
cabin <- r_score %>%  drop_na() %>% 
  group_by(airline) %>% 
  transmute(Overall_cabin= seat_comfort + cabin_service + food_bev + entertainment)%>%
  summarise(Overall_cabin_mean = mean(Overall_cabin)) %>%
  arrange(desc(Overall_cabin_mean)) %>%  head(20)

ggplot(cabin,aes(x=reorder(airline,-(Overall_cabin_mean)),y=Overall_cabin_mean))+
  geom_bar(width=.5,stat = "identity")+
  coord_flip()

scale y duzenle

```

```{r Value for Money}

value_money <- r_score %>% drop_na() %>%  
  group_by(airline) %>% 
  summarise(value_of_money=mean(value_for_money)) %>% 
  arrange(desc(value_of_money)) %>% head(20)


ggplot(value_money,aes(x=reorder(airline,-(value_of_money)),y=value_of_money))+
  geom_bar(width=.5,stat = "identity")+
  coord_flip()
  

to_do value ve over all ayni grafikte nasil gosteririm


```


```{r}


```
